Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-04-26 R/CONUS_AOD.Rmd
map noaa regions

```{r strata_noaa_regions, echo=FALSE, fig.pos="H"}
# performance by NOAA climate regions
result <- dt[, performance_aod(.SD), keyby = state.noaa.region]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")

## map by NOAA regions
# map_regions <- ggplot(conus) + geom_sf()
# print(map_regions)
```

>>>>

```{r strata_noaa_regions, echo=FALSE, fig.pos="H"}
# performance by NOAA climate regions
result <- dt[, performance_aod(.SD), keyby = state.noaa.region]
kbl(result, col.names = gsub(pattern = "\\.|_", " ", names(result))) %>% 
  kable_styling(latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1cm")
```

```{r noaa_region_plot, echo=FALSE, dev='png', dpi=300}
## map of performance by NOAA regions
conus$state.noaa.region <- factor(
   sapply(conus$STUSPS, USE.NAMES = F,
       function(sa) if (sa %in% c("AK", "HI")) NA else
           names(noaa.regions)[which(sapply(noaa.regions, function(r)
               sa %in% r))]),
   levels = names(noaa.regions))
conus <- merge(conus, dt[, performance_aod(.SD), keyby = state.noaa.region], by = "state.noaa.region")
conus_melt <- melt(as.data.table(conus[, c("geometry", "state.noaa.region", "RMSE_raw", "RMSE_pred")]),
                   id.vars = c("geometry", "state.noaa.region"))
levels(conus_melt$variable) <- c("MCD19A2", "corrected AOD")
map_region_rmse <- ggplot(conus_melt, aes(geometry = geometry)) + 
  geom_sf(aes(fill = value)) + 
  geom_sf(data = dt[, .(.N, geometry = geometry[1]), by = Site_Name], aes(geometry = geometry, size = N), alpha = 0.1) + 
  facet_wrap(~variable, ncol = 1) + 
  scale_size("colocated\nobservations", range = c(1, 3)) + 
  scale_fill_continuous("Regional\nRMSE") + 
  theme_minimal()
map_region_rmse
```
